---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# waposhosh 

<!-- badges: start -->
<!-- badges: end -->

Use R to access Washington Post School Shootings dataset. Provides convenient functions to spend less time data wrangling and more time generating findings.

## Installation

You can install the development version of waposhosh from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/waposhosh")
```

## Example

This is a basic example which shows you how to interact with the dataset:

```{r example, message = FALSE}
library(waposhosh)
library(dplyr)
## basic example code
tail(schoolshootings, 4)
```

```{r glimpse, message = FALSE}
glimpse(schoolshootings)
```

You can use latest_data() to get the latest dataset from the Washington Post [Github repo](https://github.com/washingtonpost/data-school-shootings).

```{r latest, message = FALSE}
# get latest data
latest <- latest_data()
tail(latest, 4)
```

## Credit
Credit goes to the Washington Post and their research and reporting/database development team for compiling and sharing the dataset on their [Github repo](https://github.com/washingtonpost/data-school-shootings).

### Note
The data was originally published under an Attribution-NonCommercial-ShareAlike 4.0 International (CC BY-NC-SA 4.0) license.

